---
title: "TwitterAnalytics"
author: "Vijayvithal"
date: "January 1, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
rm(list=ls())
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(rtweet)
library(text2vec)
library(igraph)
library(knitr)
knitr::opts_knit$set(root.dir = normalizePath('../'))
knitr::opts_chunk$set(fig.width=4, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE)
options(digits=4,scipen = 9)
lakh<-100000
crore<-100*lakh
lakhcrore<-lakh*crore
```

## What did the politicians say in 2016?

What views were expressed by them?
What views were endorsed by them?
What views were expressed by their friends?
Who are the "influencers"?

Politicians analysed are the PM, the President, the Union cabinet, and leaders of major political parties (Congress,CPI-M,AAP)

## Analysis method.

* We get the last 3000 tweets by each of the politicians.
* Select those tweets made in 2016.
* Eliminate all verbs and words less than 4 characters 
* Seperate out tweets from retweets,
```{r getData,cache=T}
# TBD
#	* Check people mentioned.
#	* Download their friend list.
#	* Check the last 100 tweets made by their first 100 friends.


#Check if data is already downloaded
#Add later "yadavakhilesh","GopinathMunde1","Kiren_Rijiju", "harsimrat_badal","RashtrapatiBhvn",
politicians<-unique(c( "RailMinIndia", "MoHFW_INDIA", "TexMinIndia", "HRDMinistry", "HMOIndia", "CimGOI", "manojsinhabjp", "kpgurjarbjp", "Rao_InderjitS", "DVSBJP", "shripadynaik", "rsprasad", "RadhamohanBJP", "arunjaitley", "dpradhanbjp", "Gen_VKSingh",  "MVenkaiahNaidu", "umasribharti", "rajnathsingh", "PiyushGoyal", "UK4Bihar", "PrakashJavdekar", "tourismgoi", "jualoram",  "PMOIndia", "KalrajMishra", "AnanthKumar_BJP", "PIB_India", "SushmaSwaraj", "DrJitendraSingh", "sureshpprabhu", "smritiirani", "santoshgangwar", "nitin_gadkari", "drharshvardhan",  "Ra_THORe", "nsitharaman", "narendramodi", "irvpaswan","narendramodi","OfficeOfRG","ArvindKejriwal"))
#politicians<-c("narendramodi")
for(pol in politicians){
  print (pol)
  destfile<-paste0("../data/",pol,".tweet")
  destfilesuffix<-paste0("data/",pol,".tweet.tweets.csv")
  if(!file.exists(destfilesuffix)){
    timeline<- get_timeline(pol, n = 4000, max_id = NULL, parse = TRUE,
                            clean_tweets = TRUE,lang="en")
    save_as_csv(timeline,destfile)
  }
  
}
#Perform any required cleanup.
```

Who is most active on twitter? What is original vs retweet ratio?
How does a leader use his twitter account? for self? for common cause? for Office?
Who gets a retweet?
Who gets a reply?
who gets a mention in original tweet?






```{r childknits}
src <- lapply(politicians, function(pol){knit_expand(file = "src/pol-Tweets.Rmdx")})
```
`r knit(text = unlist(src))`

# Influence matrix.

Influence can be measured by seeing who gets retweeted, who gets a reply and who gets mentioned in orignal tweets.
```
  clean_influencers<-influencers%>%
  select(screen_name, mentions_screen_name, text, in_reply_to_screen_name)  %>%
  rowwise()%>%
  mutate(retweetid=ifelse(grep("^RT \\S*:.*",text,perl=T),gsub("^RT (\\S*):.*","\\1",text,perl=F),NA)) %>%
  separate(mentions_screen_name, c("s1","s2","s3","s4","s5","s6","s7","s8","s9","s10", sep=","))%>%
  gather(scol,mentions,s1,s2,s3,s4,s5,s6,s7,s8,s9,s10)

edges<-clean_influencers%>%
  select(screen_name,mentions)%>%
  rename(from=screen_name,to=mentions)%>%
  filter(from!=to)%>%
  filter(nchar(to)>2)
pruned<-edges%>%
  group_by(from,to)%>%
  summarise(weight=n())%>%
  arrange(desc(weight))
top<-pruned%>%
  ungroup%>%
  group_by(from)%>%
  top_n(20,weight)%>%
  ungroup()
top$from<-as.character(top$from)
g<-graph_from_data_frame(top)#%>%filter(from=="narendramodi"))
#E(g)$weight<-1

g.sim<-simplify(g)
E(g.sim)$curved<-.4
E(g.sim)$label<-E(g.sim)$weight
E(g.sim)$arrow.width <- 0.1*E(g.sim)$weight 
l <- layout_in_circle(g.sim)
plot(g.sim)#,edge.width=0.2*E(g.sim)$weight,vertex.size=44,layout=l)
layouts <- grep("^layout_", ls("package:igraph"), value=TRUE)[-1] 
layouts <- layouts[!grepl("bipartite|merge|norm|sugiyama|tree", layouts)]

for (layout in layouts) {

  print(layout)

  l <- do.call(layout, list(g.sim)) 

  plot(g.sim, layout=l, main=layout,rescale=T, asp = 0, vertex.size = 5, vertex.label.cex = 0.8) 
  }
#maxwidth<-max(edges$penwidth)
#edges<-edges[complete.cases(edges),]
#%>%mutate(penwidth=1+5*penwidth/maxwidth)
#plot(g.sim,edge.width=0.2*E(g.sim)$weight,vertex.size=44,layout=l)
```
