---
title: "Twitter Activity Analysis"
author: "Vijayvithal"
date: "January 1, 2017"
output: 
  html_document 
params:
    pol: narendramodi
---
```{r setup, include=FALSE}
#rm(list=ls())
library(dplyr)
library(tidyr)
library(lubridate)
library(rtweet)
library(knitr)
library(ggplot2)
library(text2vec)
library(igraph)
knitr::opts_knit$set(root.dir = normalizePath('../'))
knitr::opts_chunk$set(fig.width=4, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE)
options(digits=4,scipen = 9)
lakh<-100000
crore<-100*lakh
lakhcrore<-lakh*crore
pol<-params$pol
destfile<-paste0("data/",pol,".tweet")
destfilesuffix<-paste0("data/",pol,".tweet.tweets.csv")
if(!file.exists(destfilesuffix)){
  timeline<- get_timeline(pol, n = 4000, max_id = NULL, parse = TRUE,
                          clean_tweets = TRUE,lang="en")
  save_as_csv(timeline,destfile)
}

```

```{r functions }
#Setup reusable functions

clean<-function(tweets){
clean_tweets <-tweets%>%
mutate(created_at=ymd_hms(created_at),week=week(created_at),yday=yday(created_at),wday=wday(created_at))%>%
	filter(created_at>=ymd("2016-01-01"))%>%
	filter(created_at<=ymd("2016-12-31"))%>%
	filter(is_retweet=="FALSE")
}


median_daily<-function(clean_tweets) {
median((clean_tweets%>%group_by(yday)%>%summarise(count=n()))$count)
}

plotfrequency<- function(clean_tweets) {
weeklyRetweet<-(clean_tweets%>%group_by(week)%>%summarise(tweet_count=n(),retweet=median(retweet_count),favorite=median(favorite_count)))%>%gather(activity,value,tweet_count,retweet,favorite)
ggplot(weeklyRetweet,aes(x=week,y=value,color=activity) ) +geom_line()+ggtitle("tweets Popularity (retweets)")
}


sayCloud<- function (tweets) {
	orig_tweets<-tweets%>%filter(is_retweet==FALSE)
if(NROW(orig_tweets>0)) {
		tokens<-itoken(as.character(iconv(orig_tweets$text,"UTF-8","ASCII",sub="")),preprocessor=tolower,tokenizer=word_tokenizer,ids=orig_tweets$status_id,progressbar = F)
		voc<-create_vocabulary(tokens,stopwords = tm::stopwords("english"))
		clean_terms<-voc$vocab%>%filter(!grepl("^0",terms,perl=T))%>%filter(nchar(terms)>3)%>%filter(terms!="https")%>%arrange(desc(terms_counts))%>%head(n=100)
		wordcloud2::wordcloud2(clean_terms)
}
}

peopleCloud<-function(peopleList){
	tbl<-table(peopleList)
if(NROW(tbl>0)){
		wordcloud2::wordcloud2(tbl)
}
}

retweetCloud<- function (tweets){
	retweet<-tweets%>%filter(is_retweet==" TRUE")
		if(NROW(retweet>0)){
			tokens<-itoken(as.character(iconv(retweet$text,"UTF-8","ASCII",sub="")),preprocessor=tolower,tokenizer=word_tokenizer,ids=retweet$status_id,progressbar = F)
				voc<-create_vocabulary(tokens,stopwords = tm::stopwords("english"))
				clean_terms<-voc$vocab%>%filter(!grepl("^0",terms,perl=T))%>%filter(nchar(terms)>3)%>%filter(terms!="http")%>%filter(terms!="https")%>%arrange(desc(terms_counts))%>%head(n=100)
				wordcloud2::wordcloud2(clean_terms)
		}

}

```

```{r cleanup }
users<-read.csv(paste0("data/",pol,".tweet.users.csv"))
tweets<-read.csv(paste0("data/",pol,".tweet.tweets.csv"),stringsAsFactors=F)
clean_tweets<-clean(tweets)
  clean_influencers<-clean_tweets%>%
  select(screen_name, mentions_screen_name, text, in_reply_to_screen_name)  %>%
  rowwise()%>%
  mutate(retweetid=ifelse(grep("^RT \\S*:.*",text,perl=T),gsub("^RT (\\S*):.*","\\1",text,perl=F),NA)) %>%
  separate(mentions_screen_name, c("s1","s2","s3","s4","s5","s6","s7","s8","s9","s10", sep=","))%>%
  gather(scol,mentions,s1,s2,s3,s4,s5,s6,s7,s8,s9,s10)
name<-users$name[1]
screenid<-users$screen_name[1]
followers<-users$followers_count[1]
desc<-users$description[1]
originalPercentage<-100*NROW(clean_tweets)/NROW(tweets)
quotes<-clean_tweets%>%filter(is_quote_status!="FALSE")
quotesPercentage<-100*NROW(quotes)/NROW(clean_tweets)
mentions<-as.character(na.omit(unlist((clean_tweets%>%filter(mentions_screen_name!="NA"))$mentions_screen_name)))

mention_tweets<-length(mentions)
mention_people<-unlist(strsplit(mentions,","))
tbl<-table(mention_people)
unique_mention_people<-length(unique(mention_people))

```

# `r name`

`r desc`

<div class="row">
<div class="col-md-6">
```{r}
plotfrequency(clean_tweets)
```

## Twitter activity
</div>


<div class="col-md-6">
## Basic tweet Stastics

* Median of `r median_daily(clean_tweets)` original tweets per day.
* `r originalPercentage`% of tweets are original tweets rest are retweets.
* `r quotesPercentage`%  tweets of the original tweets are replies to other tweeters
* `r followers` followers

</div>
</div>

<div class="row">
<div class="col-md-6">

## Tweets by `r name`
```{r}
sayCloud(tweets)
```
</div>
<div class="col-md-6">

## Retweets by `r name`
```{r}
if(NROW(clean_tweets)<NROW(tweets)){
retweetCloud(tweets)
}
```

</div>
</div>
<div class="row">
<div class="col-md-6">

## People mentioned in tweets
```{r}
peopleCloud(mention_people)
```

</div>
<div class="col-md-6">

## People Retweeted

```{r}
if(NROW(clean_tweets)<NROW(tweets)){
peopleCloud(table(na.omit(clean_influencers$retweetid)))
}else {print ("No Retweets")}

```
</div>
</div>

